Eleven years of student replication projects provide evidence on the correlates of replicability in psychology

### 2023-04-05 paper/manuscript.tex
more intro

\hypertarget{todo-list}{%
\section{TODO list}\label{todo-list}}

\begin{itemize}
\tightlist
\item
  BETTER abstract
\item
  many citations everywhere
\item
  long list of things to gesture at in intro
\item
  link to open stuffs
\item
  ** verify code for ES ** with someone
\item
  redo intro
\item
  redo results
\item
  redo discussion
\item
  fill in todos
\end{itemize}

\hypertarget{text-slush-pile}{%
\section{Text slush pile}\label{text-slush-pile}}

{[}who knows where this paragraph should go{]} Replications are one way of approximating whether an effect in the target paper is true, and how likely results are to replicate in some sort of platonic ideal world. There is no one answer here; replication projects measure something else that could be treated as an approximation. However, what a replication is really measuring is how likely it to get that effect given some conditions. Which the right conditions are is a potential point of contention (see discussion around closeness and sample size, power etc). Here, we are explicit in what sample of replicators and replication conditions were are sampling, and thus what we can generalize to. We are estimating how likely replication is when done online by a graduate student, under constraints that are typical for graduate students (limited time, limited budget). As much of scientific process is in fact performed by graduate students, we think this in itself is an interesting question.

We do not interpret our results as saying that all non-replications were false positives (presumably some are replicable under other circumstances and others are not). Some of the factors we look at are more easily interpreted as being about the original study than others. We do not assign causal explanation to the predictors because there are multiple plausible interpretations: they could be correlates of QRPs in the original, they could be correlates of harder-to-detect or more fragile effects, they could be correlates of less-close replications, they could even be correlates of another stronger predictor.

{[} there is controversy here, but to even discuss it, we need empirics{]} Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable. Lewandowsky \& Oberauer (\protect\hyperlink{ref-lewandowsky2020}{2020})

circle back to the idea that student replications (either as class or before extension into their own work) would be valuable

\hypertarget{citation-slush-pile}{%
\section{Citation slush pile}\label{citation-slush-pile}}

predict w/ ML Altmejd et al. (\protect\hyperlink{ref-altmejd2019}{2019})

econ also has replications and issues Camerer et al. (\protect\hyperlink{ref-camerer2016}{2016})

moving goal posts around replication / interpreting results Nosek \& Errington (\protect\hyperlink{ref-nosek2020}{2020})

some sort of modeling of replications Pawel \& Held (\protect\hyperlink{ref-pawel2020}{2020})

Gilbert et al. (\protect\hyperlink{ref-gilbert2016}{2016}) Anderson et al. (\protect\hyperlink{ref-anderson2016}{2016}) people argue a lot about how to interpret RPP

Schmidt (\protect\hyperlink{ref-schmidt2009}{2009}) early theory of replication as part of advancing knowledge

Simonsohn (\protect\hyperlink{ref-simonsohn2015}{2015}) small telescopes

Gelman (\protect\hyperlink{ref-gelman2018}{2018/ed}) Don't characterize replications as successes or failures.

Mathur \& VanderWeele (\protect\hyperlink{ref-mathur2020}{2020}) other metrics of replicability

pedagogy for replication in intro:

Frank \& Saxe (\protect\hyperlink{ref-frank2012}{2012})
Hawkins et al. (\protect\hyperlink{ref-hawkins}{n.d.})

O'Donnell et al. (\protect\hyperlink{ref-odonnell2021}{2021}) reps of some set of related things

Wagge et al. (\protect\hyperlink{ref-wagge2019}{2019}) get UGs to do replications for

Quintana (\protect\hyperlink{ref-quintana2021}{2021}) do reps as honors thesis
Pownall et al. (\protect\hyperlink{ref-pownall2021}{2021}) sips 2021 on teaching openness
Jekel et al. (\protect\hyperlink{ref-jekel2020}{2020}) teach open science w/ replication
Jern (\protect\hyperlink{ref-jern2018}{2018}) in one study didn't show critical thinking benefits for students to make them do replications

@@

Replicability is a desirable feature for any study that we build theory or future experiments off of. It's a pre-requisite for building theories that we have phenomena for these studies to explain, but results that cannot be observed consistently aren't results to build theories around. However, to be a load-bearing empirical result, a study needs to do much more than just replicate, it also needs to be interesting, have a believable theoretical interpretation, generalize appropriately, and have reliable constructs.

replication is important (but not everything) - good starting place
* prereq of theory building that the results of interest ``can be observed consistently''
* but not everything (can still have other problems)

The replication rates in psychology are low, and
replication rates are low in psychology (see studies)

big open question: why

experimental and correlational approaches to answering it

experimental is hard - protzko, ML5 etc. but they are expensive and you can't do them for many research questions

correlational has been pursued extensively, but is overfit to small data (prediction markets / ML models / regression of all types)

our contribution: provide more data!
using pedagogical replications, which are good because they're p(build on)
slightly different estimand but maybe a better one?

Psychology is in the middle of heated debate over its research practices and the subject of many reform efforts. Many of these issues concern how trustworth the published literature is (or isn't), how it got to be this way, and what measures can be taken to improve the quality of findings for the future. These issues center around issues of reproducibility and replicability. Concerns about replication rates have become a large point of discussion in psychology and other fields, with large scale replications spurring these discussions and providing the empirical data analyzed by all sides.

A major concern is that published literature may not replicate as much as previously thought or as desired. This has been illustrated by prominent findings/theories not replicating at all (ego depletion/ TMT?). To understand how replicable the literature as a whole is, we need empirical data about replication attempts across a wide range of studies. Most replications are targeted replications of individual results of interest to the researcher, but these are not sampled randomly from the literature, are performed in inconsistent ways, and may be selectively published depending on the results. Thus, they are not ideal for estimating the overall replicability of the field.

There have been a limited number of large-scale replication efforts, which sample studies from a discipline to estimate overall replicability. Due to the arduous process of replicating many studies, there have not been many large-scale replication efforts. Thus, all of the argumentation around predictors of replications and field-wide replication rates is fit to a small number of data points.

\hypertarget{prior-literature}{%
\subsection{prior literature}\label{prior-literature}}

We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature. RP:P sampled roughly 100 studies from top psychology journals in 2008 (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}). They found an overall replication rate around 40\%, which provided evidence to support growing concerns about the non-reliability of the literature. The RP:P dataset was itself much discussed and reanalyzed (\protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al. 2016}, \protect\hyperlink{ref-patil2016}{Patil et al. 2016}) {[}idk, maybe worth framing that this was a big deal study when it came out{]}. TODO some discussion of how many papers have reanalysed this cutting the data different ways.

The ManyLabs series of studies have also done large-scale replications of effects from psychology. Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focusing on short studies with only two conditions. Across Many labs 1-3 foo bar replicated (\protect\hyperlink{ref-klein2014}{Klein et al. 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al. 2016}, \protect\hyperlink{ref-klein2018}{Klein et al. 2018}). Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10 (\protect\hyperlink{ref-ebersole2020}{Ebersole et al. 2020}). TODO look up details

Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) replicated the 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment. They found a roughly 60\% replication rate.

\hypertarget{predictors}{%
\subsection{predictors}\label{predictors}}

In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success. Blah blah stakeholders and resources. Scientists may want to build their work on studies that are likely to replicate, so that they can replicate and build on work without wasting resources. Similarly investing in interventions may want to start with things that are more likely to replicate. There's some signal here, as people are able to predict replication success at above chance CITATIONS (\protect\hyperlink{ref-dreber2015}{Dreber et al. 2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al. 2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al. 2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al. 2019})

RP:P looked at how replication rates varied across subsamples of their studies (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}). They found that cognitive psychology studies replicated at higher, but still low rates (50\% v 25\%) compared to social psychology. They also found that larger effect sizes and smaller p-values of original studies were predictive of replicating. TODO do we talk about any other correlates.

There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences. TODO maybe foreshadow that there are reasons to believe there are correlations!

While many replications of individual studies are conducted, these may have been selected for non-representative reasons, such as a high prior on replicating (e.g.~as a demonstration), or a low or uncertain prior (e.g.~for a high-value study). When sampling is likely related to replicability, the studies are less good for estimating base rates and predictors of replicability in the literature as a whole.

\hypertarget{current-work}{%
\subsection{current work}\label{current-work}}

one strategy for the pedagogical bit at end of intro: stress ``this is what people want to do, that is, pick up a project that they care about (not a random sample of the literature) and see if they can `get it to work'\,'' - and ``subjective replication success is our primary measure for the same reason\ldots.''

can even cite the ``science is not a signal detection problem'' paper on not randomly sampling from the literature.

Prior approaches to replicability have focused on a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable. Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (van bavel etc.) or even time period (ramscar).

Further, the methods for estimating this quantity have been theoretically problematic. Sampling schemes for prior work typically does not reflect a random sample from the literature -- and even if they did, arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (``Science is not signal detection'' ref).

In contrast, we have pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they feel that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation. SPELL OUT SAMPLING DIFFERENCE AND SUCCESS DIFFERENCE.

We estimate this quantity in the context of a particular pedagogical situation: that of a graduate student entering a doctoral program in psychology\ldots{}

Prior literature, such as Frank \& Saxe (\protect\hyperlink{ref-frank2012}{2012}) and Hawkins et al. (\protect\hyperlink{ref-hawkins}{n.d.}) have advocated using research methods classes to conduct replications, both for the education and scientific value.

Here we introduce a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology. These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects. This approximately doubles the set of experiments in the large-scale replication literature. We investigate predictors of replicability in this new dataset.

@@

TODO discuss more about why this one and what other measure we don't choose are

We used a subjective rating of replication success as our primary outcome measure. The instruction team had coded a holistic measure of replication success for each project when they were turned in at the end of the course. For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (25.5681818 \% of cases). This measure was applicable across the range of statistical measures and reporting practices and accommodated studies where there were multiple important outcome measures.

As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (138 cases, see Figure \ref{fig:prisma}). We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al. 2021}).

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-altmejd2019}{}}%
Altmejd A, Dreber A, Forsell E, Huber J, Imai T, Johannesson M, Kirchler M, Nave G, Camerer C (2019) Predicting the replicability of social science lab experiments. \emph{PLOS ONE} \textbf{14}:e0225826. doi:\href{https://doi.org/10.1371/journal.pone.0225826}{10.1371/journal.pone.0225826}

\leavevmode\vadjust pre{\hypertarget{ref-anderson2016}{}}%
Anderson CJ, Bahník Š, Barnett-Cowan M, Bosco FA, Chandler J, Chartier CR, Cheung F, Christopherson CD, Cordes A, Cremata EJ, Della Penna N, Estel V, Fedor A, Fitneva SA, Frank MC, Grange JA, Hartshorne JK, Hasselman F, Henninger F, Hulst M van der, Jonas KJ, Lai CK, Levitan CA, Miller JK, Moore KS, Meixner JM, Munafò MR, Neijenhuijs KI, Nilsonne G, Nosek BA, Plessow F, Prenoveau JM, Ricker AA, Schmidt K, Spies JR, Stieger S, Strohminger N, Sullivan GB, Aert RCM van, Assen MALM van, Vanpaemel W, Vianello M, Voracek M, Zuni K (2016) Response to {Comment} on {``{Estimating} the reproducibility of psychological science.''} \emph{Science} \textbf{351}:1037--1037. doi:\href{https://doi.org/10.1126/science.aad9163}{10.1126/science.aad9163}

\leavevmode\vadjust pre{\hypertarget{ref-camerer2016}{}}%
Camerer CF, Dreber A, Forsell E, Ho T-H, Huber J, Johannesson M, Kirchler M, Almenberg J, Altmejd A, Chan T, Heikensten E, Holzmeister F, Imai T, Isaksson S, Nave G, Pfeiffer T, Razen M, Wu H (2016) Evaluating replicability of laboratory experiments in economics. \emph{Science} \textbf{351}:1433--1436. doi:\href{https://doi.org/10.1126/science.aaf0918}{10.1126/science.aaf0918}

@@

\leavevmode\vadjust pre{\hypertarget{ref-jekel2020}{}}%
Jekel M, Fiedler S, Allstadt Torras R, Mischkowski D, Dorrough AR, Glöckner A (2020) How to {Teach Open Science Principles} in the {Undergraduate Curriculum}---{The Hagen Cumulative Science Project}. \emph{Psychol Learn Teach} \textbf{19}:91--106. doi:\href{https://doi.org/10.1177/1475725719868149}{10.1177/1475725719868149}

\leavevmode\vadjust pre{\hypertarget{ref-jern2018}{}}%
Jern A (2018) A preliminary study of the educational benefits of conducting replications in the classroom. \emph{Scholarsh Teach Learn Psychol} \textbf{4}:64--68. doi:\href{https://doi.org/10.1037/stl0000104}{10.1037/stl0000104}

@@

\leavevmode\vadjust pre{\hypertarget{ref-lewandowsky2020}{}}%
Lewandowsky S, Oberauer K (2020) Low replicability can support robust and efficient science. \emph{Nat Commun} \textbf{11}:1--12. doi:\href{https://doi.org/10.1038/s41467-019-14203-0}{10.1038/s41467-019-14203-0}

@@

\leavevmode\vadjust pre{\hypertarget{ref-nosek2020}{}}%
Nosek BA, Errington TM (2020) The best time to argue about what a replication means? {Before} you do it. \emph{Nature} \textbf{583}:518--520. doi:\href{https://doi.org/10.1038/d41586-020-02142-6}{10.1038/d41586-020-02142-6}

\leavevmode\vadjust pre{\hypertarget{ref-odonnell2021}{}}%
O'Donnell M, Dev AS, Antonoplis S, Baum SM, Benedetti AH, Brown ND, Carrillo B, Choi AL, Connor P, Donnelly K, Ellwood-Lowe ME, Foushee R, Jansen R, Jarvis SN, Lundell-Creagh R, Ocampo JM, Okafor GN, Azad ZR, Rosenblum M, Schatz D, Stein DH, Wang Y, Moore DA, Nelson LD (2021) Empirical audit and review and an assessment of evidentiary value in research on the psychological consequences of scarcity. \emph{Proc Natl Acad Sci USA} \textbf{118}:e2103313118. doi:\href{https://doi.org/10.1073/pnas.2103313118}{10.1073/pnas.2103313118}

@@

\leavevmode\vadjust pre{\hypertarget{ref-pawel2020}{}}%
Pawel S, Held L (2020) Probabilistic forecasting of replication studies. \emph{PLOS ONE} \textbf{15}:e0231416. doi:\href{https://doi.org/10.1371/journal.pone.0231416}{10.1371/journal.pone.0231416}

\leavevmode\vadjust pre{\hypertarget{ref-pownall2021}{}}%
Pownall M, Azevedo F, Aldoh A, Elsherif M, Vasilev M, Pennington CR, Robertson O, Tromp MV, Liu M, Makel MC, Tonge N, Moreau D, Horry R, Shaw J, Tzavella L, McGarrigle R, Talbot C, Parsons S (2021) Embedding open and reproducible science into teaching: {A} bank of lesson plans and resources. \emph{Scholarsh Teach Learn Psychol}:No Pagination Specified--No Pagination Specified. doi:\href{https://doi.org/10.1037/stl0000307}{10.1037/stl0000307}

@@

\leavevmode\vadjust pre{\hypertarget{ref-schmidt2009}{}}%
Schmidt S (2009) Shall we {Really} do it {Again}? {The Powerful Concept} of {Replication} is {Neglected} in the {Social Sciences}. \emph{Rev Gen Psychol} \textbf{13}:90--100. doi:\href{https://doi.org/10.1037/a0015108}{10.1037/a0015108}

>>>>

@@

When building a stone wall, it's important that the components be stones that will retain their shape and not clots of dirt and sand that might fall apart and bring the rest of the wall falling down. Building a cumulative body of scientific theories similarly requires that the empirical results, especially the more foundational empirical results, be sturdy. Results that cannot be observed consistently are like dirt clots, they don't hold their shape and thus are not a strong foundation for the theories and studies built on top of them. Replications and the theory of replicability can be thought of as a way of testing whether the empirical results are sturdy. Replicating is a necessary feature for load-bearing empirical results. We note that replicability is not the only desirable feature of a study, and that replicating does not mean that a study is valid, or generalizable, or interesting.

A major concern in psychology, as in other fields, is that the published literature may not replicate as well as had previously been assumed. This is illustrated both by a few prominent findings that turn out to not replicate at all (CITE ex ego depletion, TMT), and by large-scale replication projects such as RP:P which found a replication rate around 40\% for a sample of the psychology literature (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}). This low replication rates seems undesirable and seems to run counter to the idea of a cumulative science.

A big open question is why the replication rates in psychology are so low. There are theoretical approaches modelling how questionable research practices (which many psychologists admit to) and a bias towards positive results would lead to a high rate of (non-replicable) false positives in the literature (CITE). There's some disconnect between these theoretically causal factors and empirical results about what causes or correlates with replicability.

A couple studies have attempted to intervene on the low replication rate, but seeing if certain factors can affect whether studies replicate. For instance, across 16 studies, Protzko et al. (\protect\hyperlink{ref-protzko2020}{2020}) showed that better methodological practices, such as transparency, large sample sizes, and confirmatory tests, led to replication rates that matched theoretical expectations based on the effect sizes and sample sizes, and replication effect sizes comparable with the original. Many Labs 5 examined how adding expert advice to a replication process might intervene to improve the replicate rate, and found that it mostly didn't, at least on the 10 studies they looked at (\protect\hyperlink{ref-ebersole2020}{Ebersole et al. 2020}). These types of experiments are valuable, but they aren't very scalable because they are expensive and some potential influences on non-replication are not experimentally manipulable.

As an alternative, much of the work looking at predictors of replicability has been correlation: whether using regression models, prediction markets, or machine learning techniques to build predictions about what will replicate. However, all of these approaches depend on data from replications. While many replications have been conducted, most were not randomly sampled and are not pooled together, so these studies instead rely on the small number of data points from large-scale replication projects. The RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al. 2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al. 2016}, \protect\hyperlink{ref-patil2016}{Patil et al. 2016}). These correlational approaches have established that people can predict what studies will replicate above chance (\protect\hyperlink{ref-dreber2015}{Dreber et al. 2015}, \protect\hyperlink{ref-camerer2018}{Camerer et al. 2018}, \protect\hyperlink{ref-forsell2019}{Forsell et al. 2019}, \protect\hyperlink{ref-hoogeveen2019}{Hoogeveen et al. 2019}), but have not identified that many concrete predictors that differentiate replications from non-replications. In the RP:P sample, studies in cognitive psychology (as opposed to social psychology) and studies with larger effect sizes and smaller p-values were more likely to replicate.

This reliance on the same small set of data is problematic, as much of what we think we know about replicability is overfit to this small sample. However, given the time-consuming nature of running a large number of replications, there is a limited amount of large-scale replication data to draw on. We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature. RP:P sampled roughly 100 studies from articles published in three top psychology journals in 2008 and found a overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Consortium 2015}). The ManyLabs series of replications investigating heterogeneity has sampled target studies that are short and compare only two conditions, which is not representative of the psychology literature as a whole. Across Many Labs 1-3, 29 of 51 target effects (57\%) were found to replicate (\protect\hyperlink{ref-klein2014}{Klein et al. 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al. 2016}, \protect\hyperlink{ref-klein2018}{Klein et al. 2018}). Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) found a roughly 60\% replication rate when they replicated all 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment. Those are all the large-scale replication projects of experimental psychology results available at this time. These roughly 170 results are heavily represented in the work predicting what effects will replicate.

The perceived need for more replications in tension with the lack of publishing incentives for doing replications led several to suggest that pedagogical replications could fill this gap. Doing replications is a way for students to learn to do experiments in a scaffolded way and leads to more useful results than what students could design from scratch on the same timescale (\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}, \protect\hyperlink{ref-wagge2019}{Wagge et al. 2019}, \protect\hyperlink{ref-quintana2021}{Quintana 2021}, \protect\hyperlink{ref-hawkins}{Hawkins et al. n.d.}). {[}TODO needs transition{]}

Our main contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology. These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects. This approximately doubles the set of experiments in the large-scale replication literature. We investigate predictors of replicability in this new dataset.

Prior approaches to replicability have focused on interpreting results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable. Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (CITE van bavel etc.) or even time period (CITE ramscar).

Further, the methods for estimating this quantity have been theoretically problematic. Sampling schemes for prior work typically do not reflect an entirely random sample from the literature; instead they sample from specific journals where results may be of more interest and adjust the sample for feasibility concerns. These are reasonable sampling choices, but they undermine the claim that the estimand is the level of ``truth'' in the literature as a whole. Sampling truely at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (CITE ``Science is not signal detection'' ref). How much we care about whether a study is ``trustworthy'' is not uniformly distributed across the literature.

In contrast, we have explicitly pursued a different estimand: the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.

The sampling for our replications is based on what studies students were interested in and wanted to replicate, with some constraints of feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable within their ability and budgetary constraints. Our primary criteria for replication success is a subjective measure of whether the study replicated for the same reason, that we believe this is usually what researchers care about: is it close enough that you think you're getting at the same effect and could confidently build on it. The quality of the replications also reflects this: unlike some prior work like Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}), which explicitly aimed for high-powered replications, the power in these studies was limited by budgetary reasons in some cases, which is reflective of the types of resources often available to trainee scientists.

We think this is a valuable estimand because it's estimating what people actually care about: is this result of interest sturdy enough to support cumulative science?

@@

Many different measures can be used to define replication success of an individual statistical result, and there is much discussion over what each measure represents and which make sense (\protect\hyperlink{ref-simonsohn2015}{Simonsohn 2015}, \protect\hyperlink{ref-gelman2018}{Gelman 2018/ed}, \protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}). Because we operationalized replicability as whether a study could be built upon, we used a subjective rating of replication success as our primary outcome measure. This measure has the benefit that it was applicable across the diverse range of statistical measures and reporting practices present in the sample. It, unlike statistical measures of replication, could easily accommodate studies where there were multiple important outcome measures that together defined the pattern of interest. A holistic measure of replication success had been coded for each project when it was turned in at the end of the class. For reliability, VB independently code the replication success from the replication reports; discrepancies were resolved by discussion between MCF and VB (25.5681818 \% of cases).

As a complement, we also used two statistical measure of replication on the subset of the data where they were computable (138 cases, see Figure \ref{fig:prisma}). We measured p-original, the p-value on the null hypothesis that the original and replication statistics are from the same distribution, as a continuous variable, and we also determined whether the replication statistic fell within the prediction interval of the original statistic (\protect\hyperlink{ref-errington2021}{Errington et al. 2021}). These both measure how similar the estimates from the two sets of data are.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-anderson2016}{}}%
Anderson CJ, Bahník Š, Barnett-Cowan M, Bosco FA, Chandler J, Chartier CR, Cheung F, Christopherson CD, Cordes A, Cremata EJ, Della Penna N, Estel V, Fedor A, Fitneva SA, Frank MC, Grange JA, Hartshorne JK, Hasselman F, Henninger F, Hulst M van der, Jonas KJ, Lai CK, Levitan CA, Miller JK, Moore KS, Meixner JM, Munafò MR, Neijenhuijs KI, Nilsonne G, Nosek BA, Plessow F, Prenoveau JM, Ricker AA, Schmidt K, Spies JR, Stieger S, Strohminger N, Sullivan GB, Aert RCM van, Assen MALM van, Vanpaemel W, Vianello M, Voracek M, Zuni K (2016) Response to {Comment} on {``{Estimating} the reproducibility of psychological science.''} \emph{Science} \textbf{351}:1037--1037. doi:\href{https://doi.org/10.1126/science.aad9163}{10.1126/science.aad9163}

@@

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-protzko2020}{}}%
Protzko J, Krosnick J, Nelson LD, Nosek BA, Axt J, Berent M, Buttrick N, DeBell M, Ebersole CR, Lundmark S, MacInnis B, O'Donnell M, Perfecto H, Pustejovsky JE, Roeder SS, Walleczek J, Schooler J (2020) High {Replicability} of {Newly-Discovered Social-behavioral Findings} is {Achievable}. preprint. {PsyArXiv}. Available from: \url{https://osf.io/n2a9x} {[}Last accessed 5 April 2023{]}. doi:\href{https://doi.org/10.31234/osf.io/n2a9x}{10.31234/osf.io/n2a9x}

@@
